MSK II

### 2017-09-11 msk2.rmd
fixed a few typos

| Type | Character | Time course | Radiation | NSAID response | Onset | Age |
| ------ |---------------  | ---------- | --------- | ------- |  ------ | ----- |
| Mechanical | Thinking muscular: diffuse/achey | Worse with movement PM AM | Lumbar to back of thigh | Moderate/good | Post trauma/gradual | Mid-late |
| Inflammation | Something pushing: stabbing | AM more likely than PM | To the butt | Really good | Insidious/gradual | 20s |
| Radicular | Sharp/stabbing | Worse with activity | Goes down the leg towards ankle and foot | Limited | Usually sudden | Any |
| Neuropathic | Burning | Constant, no association with activity | Towards ankle and foot | Limited | Insidious |
| Malignant | Deep gnawing contionuous ache | Constant, wakes up at night | Limited | Insidious |

@@

What are the types of spondyloarthropathies (Rheumatoid factor negative)

-  Ankylosing spondylitis: $M>F$,
-  Psoriatic arthritis: nail pitting, sausage fingers
-  Reactive arthritis: after an infn (think UTIs, STIs), $M>F$
-  IBD associated: 
-  
-

@@

-  Oseopenia
-  LOTS of CVS issues

>>>>

| Type | Character | Time course | Radiation | NSAID response | Onset | Age |
| --------- |---------------  | ---------- | --------- | ------- |  ------ | ----- |
| Mechanical | Thinking muscular: diffuse/achey | Worse with movement PM AM | Lumbar to back of thigh | Moderate/good | Post trauma/gradual | Mid-late |
| Inflammation | Something pushing: stabbing | AM more likely than PM | To the butt | Really good | Insidious/gradual | 20s |
| Radicular | Sharp/stabbing | Worse with activity | Goes down the leg towards ankle and foot | Limited | Usually sudden | Any |
| Neuropathic | Burning | Constant, no association with activity | Towards ankle and foot | Limited | Insidious |
| Malignant | Deep gnawing contionuous ache | Constant, wakes up at night | Limited | Insidious |

@@

What are the types of spondyloarthropathies (Rheumatoid factor and other antibody negative; many carry HLA-B27))

-  Ankylosing spondylitis: $M>F$,
-  Psoriatic arthritis: nail pitting, sausage fingers
-  Reactive arthritis: after an infn (think UTIs, STIs), $M>F$
-  IBD associated: 
-  Undifferentiated:

@@

-  Osteopenia
-  LOTS of CVS issues
